Threat Modeling for a Lawful Device Access Proposal

### 2021-03-03 articles/tops-acm/manuscript.tex
Add DFD syntax to TOPS article

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PAPER %
\section{Introduction}
\label{sec-intro}

% TODO: add actual intro, not just chapter intro. Take some from paper intro, but also introduce the diagram syntax

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PAPER %

% TODO: add actual intro.

\section{Threat Modeling with Data Flow Diagrams}
\label{sec-threat-model-intro}

Threat modeling is an important step in analyzing the security at the systems level. Models abstract away fine details
and focus on the architecture, processes, and dataflows in a system. They assist in the understanding of current systems
and the prevention of problems in new systems, both of which are important when facing the prospect of designing an
\ac{EA} mechanism built on top of a complex and aging technology stack.

Threat modeling begins with the questions, ``What are you building?'' and ``What can go wrong?''
\cite{shostack_threat_2014}. Accurately answering the first question is crucial, particularly for the field of
cryptography, which hinges on precise definitions of security requirements \cite{varia_2018}. The answer to the second
question depends on the types of attackers under consideration and determines the scope of threats to be considered.
``What are you building?'' hasn't been asked enough in the current phase of the \ac{EA} debate, and ``What can go
wrong?'' cannot be faithfully answered without knowing what is being built.

\Acp{DFD} were designed to address these questions. \Acp{DFD} feature processes, data flows, data stores, and external
entities. \Acp{DFD} are well-suited for threat modeling because security vulnerabilities tend to follow data flow, not
control flow \cite{shostack_threat_2014}. They are particularly well-suited for \ac{EA}, as data privacy is of primary
concern. \myfig{fig-dfd-dh-traditional} shows the basic elements of a \ac{DFD} of a simplified Diffie-Hellman key
exchange.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\linewidth]{dfds/build/diffie-hellman-traditional.png}
    \caption{A \acs{DFD} for a simplified Diffie-Hellman key exchange}
    \label{fig-dfd-dh-traditional}
\end{figure}

\Acp{DFD} show what data is transferred via labels on the flows. However, labels can be insufficient in complex
\acp{DFD}, and the method has no syntax for computation or cryptographic protocols. In order to maximize their
communicative ability in the context of encryption and \acl{EA} schemes, I introduce the additional syntax show in
\myfig{fig-dfd-dh-updated}.

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{dfds/build/diffie-hellman.png}
    \caption{A Diffie-Hellman key exchange illustrated with additional syntax}
    \label{fig-dfd-dh-updated}
\end{figure}

The new syntax illustrates the data in more detail as it is stored, transferred, and operated on. By illustrating the
data itself, it eliminates the need for labels on lines and can be used to communicate entire protocols in a single
diagram. \myfig{fig-dfd-key} contains the full set of symbols. \mysec{sec-intro} includes \acp{DFD} in this style to
analyze threats that EA would introduce.

\begin{figure}[t]
    \centering
    \includegraphics[width=0.85\linewidth]{dfds/build/dfd-key.png}
    \caption{Expanded set of DFD symbols}
    \label{fig-dfd-key}
\end{figure}

\section{Analysis Introduction}
\label{sec-intro}

% TODO: add actual intro, not just chapter intro. Take some from Thesis intro.
